Local to global N input modelling

### 2025-06-06 manuscript.qmd
Composition comparison plot, and move sensitivities to supplementaries

library(magrittr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(ggh4x)
library(here)
library(ggpubr)
library(patchwork)
library(qs)
library(arrow)
library(targets)
library(sf)
library(terra)
library(rnaturalearth)
library(rnaturalearthdata)
library(rnaturalearthhires)
library(dtplyr)
library(furrr)
library(RColorBrewer)
library(purrr)
library(future)
library(readxl)
library(units)
library(conflicted)
library(lubridate)
library(RColorBrewer)
conflicts_prefer(dplyr::select(), dplyr::filter(), dplyr::intersect(), .quiet = T)
# This markdown uses TinyTex - install with tinytex::install_tinytex()

@@

@@

df %>% 
  ggplot(aes(x = water_temp, y = ing_pot)) +
  geom_line(linewidth = 0.75) +
  geom_line(aes(y = food_prov), linewidth = 0.75, linetype = "dotted") +
  scale_y_continuous(breaks = seq(0,1.5,0.25)) +
  scale_x_continuous(breaks = seq(-5,30,5), limits = c(-5,26)) +
  labs(x = expression("Water temperature ("*degree*"C)"), y = "Relative food ingested/provided") +
  theme_classic() +
  theme(text = element_text(colour = "black", family = "serif", size = 12))
```

@@

p2 <- farm_temp_means %>% 
  ggplot(aes(y = mean_temp, x = abs(lat), colour = country)) +
  geom_point(size = 2) +
  scale_colour_brewer(palette = "Set1") +
  labs(x = expression("Absolute latitude ("*degree*")"), y = expression("Mean temperature ("*degree*"C)")) +
  theme_classic() +
  theme(legend.position = "top", legend.title = element_blank())

p3 <- farm_temp_means %>% 
  mutate(hemisphere = case_when(lat < 0 ~ "S", T ~ "N")) %>% 
  ggplot(aes(x = mean_temp, fill = hemisphere)) +
  geom_histogram(position = "identity", colour = "black", alpha = 0.5, binwidth = 0.5) +
  labs(x = expression("Mean temperature ("*degree*"C)"), y = "Frequency") +
  theme_classic() +
  theme(legend.position = "top", legend.title = element_blank())

@@

Parameter sensitivity was tested by varying each parameter in @tbl-params by $\pm 10$% and calculating sensitivity as $S_p = \frac{(P_{1.1} - P_{0.9})}{0.2 \times P_1}$, where $S$ is the sensitivity of the measured variable to changes in parameter $p$, and $P_{1.1}$, $P_{0.9}$, and $P_{1}$ are the value of the measured variable when the model is run with parameter $p$ at 110%, 90%, and 100% of its value respectively. 
* All parameters in Table @tbl-params were tested across all farms (all temperatures)
* Used the full population of 5000 for the population parameters $\overline{W}$, $\Delta{W}$, $\overline{I_{max}}$, $\Delta{I_{max}}$, $\overline{F}$, and $\Delta{F}$, and a population of 100 in each farm for all other parameters.

sens_data %>% 
  ggplot(aes(x = adj_param, y = mean_sens, ymin = mean_sens - sd_sens, ymax = mean_sens + sd_sens, fill = measure)) +
  geom_col(position = position_dodge(), width = 0.95, colour = "black", alpha = 0.75) +
  # geom_errorbar(position = position_dodge(width = 0.95), width = 0.3) +
  geom_hline(aes(yintercept = 0), linetype = "dashed") +
  scale_y_continuous(breaks = seq(-30,30,5), limits = c(-10,30)) +
  scale_x_discrete(limits = rev(param_names$name), labels = rev(param_names$lab)) +
  scale_fill_manual(values = c(weight = "salmon", total_excr = "steelblue")) +
  # scale_fill_manual(values = c("weight" = "salmon", "uneat" = "steelblue", "excr" = "darkgreen")) +
  labs(x = "Adjusted parameter", y = "Sensitivity") +
  theme_classic() + 
  theme(legend.position = "none", 
        strip.text = element_blank(), 
        aspect.ratio = 0.8,
        text = element_text(size = 12),
        axis.title.y = element_blank()) +
  coord_flip()
```

@@

contribL_1 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
tL_1 <- sum(contribL_1)
digestL <- sum(df[["Lipids"]]$digest * contribL_1)/tL_1

@@

contribL_2 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
tL_2 <- sum(contribL_2)
digestL <- sum(df[["Lipids"]]$digest * contribL_2)/tL_2

@@

contribL_3 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
tL_3 <- sum(contribL_3)
digestL <- sum(df[["Lipids"]]$digest * contribL_3)/tL_3

@@

* Feeds came from [@cottrell_origins_nodate; @cottrell_global_2020].
* The reference feed is `r round(100*tP_1,1)`% protein, `r round(100*tL_1,1)`% lipid, `r round(100*tC_1,1)`% carbohydrate. 
* The past feed is `r round(100*tP_2,1)`% protein, `r round(100*tL_2,1)`% lipid, `r round(100*tC_2,1)`% carbohydrate. 
* The future feed is `r round(100*tP_3,1)`% protein, `r round(100*tL_3,1)`% lipid, `r round(100*tC_3,1)`% carbohydrate. 
* Within the reference feed, protein is overall `r round(100*digestP_1,1)`% digestible, lipid is overall `r round(100*digestL,1)`% digestible, and carbohydrate is overall `r round(100*digestC_1,1)`% digestible.
* Within the past feed, protein is overall `r round(100*digestP_2,1)`% digestible, lipid is overall `r round(100*digestL,1)`% digestible, and carbohydrate is overall `r round(100*digestC_2,1)`% digestible.
* Within the future feed, protein is overall `r round(100*digestP_3,1)`% digestible, lipid is overall `r round(100*digestL,1)`% digestible, and carbohydrate is overall `r round(100*digestC_3,1)`% digestible.

@@

ggplot(df, aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = as.factor(cohort))) +
  geom_line(linewidth = 0.75) +
  geom_ribbon(linetype = "dotted", alpha = 0) +
  facet_grid(cols = vars(split)) +
  theme_classic() +
  scale_x_continuous(breaks = seq(0, 1600, 120)) +
  scale_colour_manual(values = cohort_pal) +
  theme(legend.position = "none") +
  labs(y = "Farm biomass", x = "Day of production")
```

@@

harv_size %>% 
  mutate(weight = weight %>% set_units("g") %>% set_units("kg")) %>% 
  select(c(farm_ID, weight)) %>% 
  ggplot(aes(x = weight)) +
  geom_histogram(binwidth = 0.25, colour = "black", fill = "salmon", alpha = 0.75) +
  scale_y_continuous(limits = c(0,500)) +
  labs(y = "Frequency", x = "Harvest weight") +
  theme_classic() +
  theme(
    legend.position = "none", 
    aspect.ratio = 0.75
  )
```

@@

coho_biom %>% 
  ggplot(aes(x = tonnes_per_farm, y = mean, colour = country)) +
  geom_point(size = 2.5) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  theme_classic() +
  scale_x_continuous(limits = c(0,1700)) +
  scale_y_continuous(limits = c(0,1700)) +
  scale_colour_brewer(palette = "Set1") +
  labs(y = "Modelled biomass produced (t)", x = "Observed biomass produced (t)") +
  theme_classic() +
  theme(legend.position = "top", legend.title = element_blank())
```

@@

@@

* Location -> temperature -> farm_ID
* Uneaten feed + excreted faeces = total inputs (g)
* Day of production (impacted by location)

* Main point is the difference between feeds (kg/t salmon).
* Also interesting to see if difference between feeds varies geographically (correlates with latitude, or maybe mean/median/max temperature?)

@@

qs::qread(farmrun_files[1]) %>% names()
weight <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["weight_stat"]]}) %>% bind_rows()
biomass <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["biomass_stat"]]}) %>% bind_rows()
```

@@

uneaten_total %>% 
  merge(farms_geometry, by = "farm_ID") %>% 
  mutate(uneat_biom_mean = uneat_biom_mean %>% set_units("g g_fish-1 d-1") %>% set_units("g kg_fish-1 d-1"),
         country = factor(country, levels = sorted_countries)) %>% 
  ggplot(aes(x = country, y = uneat_biom_mean, fill = feed)) +
  geom_boxplot() +
  theme_classic() +
  scale_fill_manual(values = feed_pal) +
  labs(y = "Uneaten feed", x = "Country")
```

@@

excreted_total %>% 
  merge(farms_geometry, by = "farm_ID") %>% 
  mutate(excr_biom_mean = excr_biom_mean %>% set_units("g g_fish-1 d-1") %>% set_units("g kg_fish-1 d-1"),
         country = factor(country, levels = sorted_countries)) %>% 
  ggplot(aes(x = country, y = excr_biom_mean, fill = feed)) +
  geom_boxplot() +
  theme_classic() +
  scale_fill_manual(values = feed_pal) +
  labs(y = "Excreted faeces", x = "Country")
```

@@

df %>% 
  ggplot(aes(x = reference, y = diff_perc, colour = hemisphere)) +
  geom_point() + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_grid(~feed) +
  theme_classic()
```

@@

df %>% 
  group_by(prod_day, feed, hemisphere) %>% 
  reframe(diff_perc_mean = meanna(diff_perc),
          diff_perc_sd = sdna(diff_perc)) %>% 
  ggplot(aes(x = prod_day, y = diff_perc_mean, ymin = diff_perc_mean-diff_perc_sd, ymax = diff_perc_mean+diff_perc_sd, 
             colour = as.factor(hemisphere), fill = as.factor(hemisphere))) +
  geom_line() + 
  geom_ribbon(alpha = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_grid(~feed) +
  theme_classic()
```

@@

df %>% 
  group_by(hemisphere, feed, prod_day) %>% 
  reframe(mean_diff = meanna(diff),
          sd_diff = sdna(diff) %>% set_units("kg t_fish-1 d-1")) %>% 
  ggplot(aes(x = prod_day, y = mean_diff, ymin = mean_diff-sd_diff, ymax = mean_diff+sd_diff, colour = hemisphere, fill = hemisphere)) +
  geom_line(linewidth = 0.75) +
  geom_ribbon(alpha = 0.25) +
  facet_wrap(~feed) +
  theme_classic()
```

@@

excreted_all <- excreted_total %>% 
  select(-contains("biom")) %>% 
  merge(excreted_P, by = c("farm_ID", "feed", "t")) %>% 
  merge(excreted_L, by = c("farm_ID", "feed", "t")) %>% 
  merge(excreted_C, by = c("farm_ID", "feed", "t")) %>% 
  select(-c(contains("sd"))) %>% 
  rename(protein = mean.x, lipids = mean.y, carbohydrates = mean) %>% 
  mutate(protein = protein/excr_mean %>% set_units("d-1"),
         lipids = lipids/excr_mean %>% set_units("d-1"),
         carbohydrates = carbohydrates/excr_mean %>% set_units("d-1")) %>% 
  select(-excr_mean)
```

Unlike the uneaten feed, the composition of excreted faeces differs from that of the incoming feed.

* Composition does not change through time or with increasing biomass (because digestibility does not change with fish size or temeprature)

```{r composition-throughtime}
#| eval: false

@@

| Macro | Reference | Past | Future |
|:-----------:|:---:|:---:|:---:|
| Protein | `r tP_1` |  `r tP_2` |  `r tP_3` | 
| Lipids | `r tL_1` | `r tL_2` |  `r tL_3` | 
| Carbohydrates | `r tC_1` | `r tL_2` |  `r tL_3` |

@@

>>>>

library(magrittr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(ggh4x)
library(here)
library(ggpubr)
library(cowplot)
library(patchwork)
library(qs)
library(arrow)
library(targets)
library(sf)
library(terra)
library(rnaturalearth)
library(rnaturalearthdata)
library(rnaturalearthhires)
library(dtplyr)
library(furrr)
library(RColorBrewer)
library(purrr)
library(future)
library(readxl)
library(units)
library(conflicted)
library(lubridate)
library(RColorBrewer)
conflicts_prefer(dplyr::select(), dplyr::filter(), dplyr::intersect(), .quiet = T)
# This markdown uses TinyTex - install with tinytex::install_tinytex()

@@

prettyplot <- function() {
  theme_classic() +
    theme(legend.position = "none",
          text = element_text(family = "serif", size = 12, colour = "black"),
          axis.title.x = element_text(vjust = 0.5),
          axis.title.y = element_text(hjust = 0.5))
}

@@

df %>% 
  ggplot(aes(x = water_temp, y = ing_pot)) +
  geom_line(linewidth = 0.75) +
  geom_line(aes(y = food_prov), linewidth = 0.75, linetype = "dotted") +
  scale_y_continuous(breaks = seq(0,1.5,0.25)) +
  scale_x_continuous(breaks = seq(-5,30,5), limits = c(-5,26)) +
  labs(x = expression("Water temperature ("*degree*"C)"), y = "Relative food ingested/provided") +
  prettyplot() +
  theme(text = element_text(colour = "black", family = "serif", size = 12))
```

@@

p2 <- farm_temp_means %>% 
  ggplot(aes(y = mean_temp, x = abs(lat), colour = country)) +
  geom_point(size = 2) +
  scale_colour_brewer(palette = "Set1") +
  labs(x = expression("Absolute latitude ("*degree*")"), y = expression("Mean temperature ("*degree*"C)")) +
  prettyplot() +
  theme(legend.position = "top", legend.title = element_blank())

p3 <- farm_temp_means %>% 
  mutate(hemisphere = case_when(lat < 0 ~ "S", T ~ "N")) %>% 
  ggplot(aes(x = mean_temp, fill = hemisphere)) +
  geom_histogram(position = "identity", colour = "black", alpha = 0.5, binwidth = 0.5) +
  labs(x = expression("Mean temperature ("*degree*"C)"), y = "Frequency") +
  prettyplot() +
  theme(legend.position = "top", legend.title = element_blank())

@@

Parameter sensitivity was tested by varying each parameter in @tbl-params by $\pm 10$% and calculating sensitivity as $S_p = \frac{(P_{1.1} - P_{0.9})}{0.2 \times P_1}$, where $S$ is the sensitivity of the measured variable to changes in parameter $p$, and $P_{1.1}$, $P_{0.9}$, and $P_{1}$ are the value of the measured variable when the model is run with parameter $p$ at 110%, 90%, and 100% of its value respectively. 
All parameters in Table @tbl-params were tested. The population-level parameters ($\overline{W}$, $\Delta{W}$, $\overline{I_{max}}$, $\Delta{I_{max}}$, $\overline{F}$, $\Delta{F}$) were tested with a population of of 5000 on a random 10% of farms, while all other parameters were tested across all farms with a population of 10.

@@

contribL_1 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
tL_1 <- sum(contribL_1)
digestL_1 <- sum(df[["Lipids"]]$digest * contribL_1)/tL_1

@@

contribL_2 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
tL_2 <- sum(contribL_2)
digestL_2 <- sum(df[["Lipids"]]$digest * contribL_2)/tL_2

@@

contribL_3 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
tL_3 <- sum(contribL_3)
digestL_3 <- sum(df[["Lipids"]]$digest * contribL_3)/tL_3

@@

* Feeds came from [@cottrell_origins_nodate; @cottrell_global_2020].
* The reference feed is `r round(100*tP_1,1)`% protein, `r round(100*tL_1,1)`% lipid, `r round(100*tC_1,1)`% carbohydrate. 
* The past feed is `r round(100*tP_2,1)`% protein, `r round(100*tL_2,1)`% lipid, `r round(100*tC_2,1)`% carbohydrate. 
* The future feed is `r round(100*tP_3,1)`% protein, `r round(100*tL_3,1)`% lipid, `r round(100*tC_3,1)`% carbohydrate. 
* Within the reference feed, protein is overall `r round(100*digestP_1,1)`% digestible, lipid is overall `r round(100*digestL_1,1)`% digestible, and carbohydrate is overall `r round(100*digestC_1,1)`% digestible.
* Within the past feed, protein is overall `r round(100*digestP_2,1)`% digestible, lipid is overall `r round(100*digestL_2,1)`% digestible, and carbohydrate is overall `r round(100*digestC_2,1)`% digestible.
* Within the future feed, protein is overall `r round(100*digestP_3,1)`% digestible, lipid is overall `r round(100*digestL_3,1)`% digestible, and carbohydrate is overall `r round(100*digestC_3,1)`% digestible.

@@

ggplot(df, aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = as.factor(cohort))) +
  geom_line(linewidth = 0.75) +
  geom_ribbon(linetype = "dotted", alpha = 0) +
  facet_grid(cols = vars(split)) +
  scale_x_continuous(breaks = seq(0, 1600, 120)) +
  scale_colour_manual(values = cohort_pal) +
  prettyplot() +
  labs(y = "Farm biomass", x = "Day of production")
```

@@

harv_size %>% 
  mutate(weight = weight %>% set_units("g") %>% set_units("kg")) %>% 
  select(c(farm_ID, weight)) %>% 
  ggplot(aes(x = weight)) +
  geom_histogram(binwidth = 0.25, colour = "black", fill = "salmon", alpha = 0.75) +
  scale_y_continuous(limits = c(0,500)) +
  labs(y = "Frequency", x = "Harvest weight") +
  prettyplot() +
  theme(aspect.ratio = 0.75)
```

@@

coho_biom %>% 
  ggplot(aes(x = tonnes_per_farm, y = mean, colour = country)) +
  geom_point(size = 2.5) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  scale_x_continuous(limits = c(0,1700)) +
  scale_y_continuous(limits = c(0,1700)) +
  scale_colour_brewer(palette = "Set1") +
  labs(y = "Modelled biomass produced (t)", x = "Observed biomass produced (t)") +
  prettyplot() +
  theme(legend.position = "top", legend.title = element_blank())
```

@@

* Parameter sensitivity results are in supplementary @sec-parameter-sensitivity

@@

* Location -> temperature -> farm_ID
* Uneaten feed + excreted faeces = total inputs (g)
* Day of production (impacted by location)
* Main point is the difference between feeds (kg/t salmon).
* Also interesting to see if difference between feeds varies geographically (correlates with latitude, or maybe mean/median/max temperature?)

@@

# qs::qread(farmrun_files[1]) %>% names()
weight <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["weight_stat"]]}) %>% bind_rows()
biomass <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["biomass_stat"]]}) %>% bind_rows()
```

@@

uneaten_total %>% 
  merge(farms_geometry, by = "farm_ID") %>% 
  mutate(uneat_biom_mean = uneat_biom_mean %>% set_units("g g_fish-1 d-1") %>% set_units("g kg_fish-1 d-1"),
         country = factor(country, levels = sorted_countries)) %>% 
  ggplot(aes(x = country, y = uneat_biom_mean, fill = feed)) +
  geom_boxplot() +
  prettyplot() +
  scale_fill_manual(values = feed_pal) +
  labs(y = "Uneaten feed", x = "Country")
```

@@

excreted_total %>% 
  merge(farms_geometry, by = "farm_ID") %>% 
  mutate(excr_biom_mean = excr_biom_mean %>% set_units("g g_fish-1 d-1") %>% set_units("g kg_fish-1 d-1"),
         country = factor(country, levels = sorted_countries)) %>% 
  ggplot(aes(x = country, y = excr_biom_mean, fill = feed)) +
  geom_boxplot() +
  prettyplot() +
  scale_fill_manual(values = feed_pal) +
  labs(y = "Excreted faeces", x = "Country")
```

@@

df %>% 
  ggplot(aes(x = reference, y = diff_perc, colour = hemisphere)) +
  geom_point() + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_grid(~feed) +
  prettyplot()
```

@@

df %>% 
  group_by(prod_day, feed, hemisphere) %>% 
  reframe(diff_perc_mean = meanna(diff_perc),
          diff_perc_sd = sdna(diff_perc)) %>% 
  ggplot(aes(x = prod_day, y = diff_perc_mean, ymin = diff_perc_mean-diff_perc_sd, ymax = diff_perc_mean+diff_perc_sd, 
             colour = as.factor(hemisphere), fill = as.factor(hemisphere))) +
  geom_line() + 
  geom_ribbon(alpha = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_grid(~feed) +
  prettyplot()
```

@@

df %>% 
  group_by(hemisphere, feed, prod_day) %>% 
  reframe(mean_diff = meanna(diff),
          sd_diff = sdna(diff) %>% set_units("kg t_fish-1 d-1")) %>% 
  ggplot(aes(x = prod_day, y = mean_diff, ymin = mean_diff-sd_diff, ymax = mean_diff+sd_diff, colour = hemisphere, fill = hemisphere)) +
  geom_line(linewidth = 0.75) +
  geom_ribbon(alpha = 0.25) +
  facet_wrap(~feed) +
  prettyplot()
```

@@

excreted_all <- excreted_total %>% 
  select(-contains("biom")) %>% 
  merge(excreted_P, by = c("farm_ID", "feed", "t")) %>% 
  merge(excreted_L, by = c("farm_ID", "feed", "t")) %>% 
  merge(excreted_C, by = c("farm_ID", "feed", "t")) %>% 
  select(-c(contains("sd"))) %>% 
  rename(protein = mean.x, lipids = mean.y, carbohydrates = mean) %>% 
  mutate(protein = protein/excr_mean %>% set_units("d-1"),
         lipids = lipids/excr_mean %>% set_units("d-1"),
         carbohydrates = carbohydrates/excr_mean %>% set_units("d-1")) %>% 
  select(-excr_mean)

ec <- excreted_all %>% 
  group_by(feed) %>% 
  reframe(P = mean(protein),
          C = mean(carbohydrates),
          L = mean(lipids)) %>% 
  mutate(source = "excreted") %>% 
  rbind(data.frame(
    feed = c("reference", "past", "future"),
    P = c(tP_1, tP_2, tP_3),
    C = c(tC_1, tC_2, tC_3),
    L = c(tL_1, tL_2, tL_3),
    source = rep("feed", 3)
  )) %>% 
  pivot_longer(cols = c(P,L,C), names_to = "macro", values_to = "value", 
               names_transform = list(macro = as.factor), values_transform = list(value = as.numeric)) %>% 
  mutate(source = factor(source, levels = c("feed", "excreted")),
         macro = factor(macro, levels = c("P", "L", "C"), labels = c("Protein", "Lipids", "Carbohydrates")),
         feed = factor(feed, levels = c("reference", "past", "future")),
         source = factor(source, levels = c("feed", "excreted"), labels = c("Feed", "Faeces")))
```

Unlike the uneaten feed, the composition of excreted faeces differs from that of the incoming feed.
[Note that composition does not change through time or with increasing biomass (because digestibility does not change with fish size or temeprature)]{.aside}

```{r composition-throughtime, class.chunk = "aside"}
#| eval: false

@@

```{r fig-composition-comparison}
#| eval: true
#| fig-cap: Comparison of the composition of the reference (blue), past (red) and future (green) feed and faeces of salmon fed each feed.

ggplot(ec, aes(x = source, y = 100*value, fill = feed)) +
  geom_col(colour = "black", position = position_dodge(width = 0.9), alpha = 0.75) +
  facet_grid(cols = vars(macro)) +
  prettyplot() +
  scale_fill_manual(values = feed_pal) +
  scale_y_continuous(breaks = seq(0, 60, 10)) +
  labs(y = "Composition (%)", x = "Source")
```

@@

# Supplementary stuff

## Parameter sensitivity {#sec-parameter-sensitivity}

sens_data %>% 
  ggplot(aes(x = adj_param, y = mean_sens, ymin = mean_sens - sd_sens, ymax = mean_sens + sd_sens, fill = measure)) +
  geom_col(position = position_dodge(), width = 0.95, colour = "black", alpha = 0.75) +
  # geom_errorbar(position = position_dodge(width = 0.95), width = 0.3) +
  geom_hline(aes(yintercept = 0), linetype = "dashed") +
  scale_y_continuous(breaks = seq(-30,30,5), limits = c(-10,30)) +
  scale_x_discrete(limits = rev(param_names$name), labels = rev(param_names$lab)) +
  scale_fill_manual(values = c(weight = "salmon", total_excr = "steelblue")) +
  # scale_fill_manual(values = c("weight" = "salmon", "uneat" = "steelblue", "excr" = "darkgreen")) +
  labs(x = "Adjusted parameter", y = "Sensitivity") +
  prettyplot() +
  theme(strip.text = element_blank(), 
        aspect.ratio = 0.8,
        axis.title.y = element_blank()) +
  coord_flip()
```
